---
title: "CreateRecordTable"
author: "Amy Van Scoyoc"
date: "9/1/2022"
output: github_document
---

# Libraries

```{r}
library(tidyverse) # for basic data wrangling
library(camtrapR) # for creating species record tables
```

# Create recordTable in camtrapR from raw folders

Before making the record table, make sure that the spelling, capitalization, and punctuation of species names are identical across camera folders, to avoid headaches down the road. 

```{r checking folder names, eval=FALSE}
setwd("/Volumes/SCIDAT_HD/SnowLeopard")
list.dirs(full.names = FALSE) -> folder_names

folder_names %>% 
  str_extract(pattern = "([^/]+$)") %>% 
  unique() %>% 
  as_tibble() %>% 
  arrange(desc(value))
```


The following code will create a record table csv with the camera, species, date, and time of every photograph taken, excluding images of nothing ("Blank").

```{r create recordTable, eval = F}
#Only need to run this once to create the record table, can read it in later
# set working directory as the folder with the camera folders in it
setwd("/Volumes/SCIDAT_HD/SnowLeopard/")


# create record table
record_table <- recordTable(inDir = "Data-21-22", # folder with the camera folders in it
                        IDfrom = "directory", # indicates that species ID corresponds to folder name
                        exclude = c("Blank"), # exclude Ghosts
                        minDeltaTime = 30, # create as independent detections
                        deltaTimeComparedTo = "lastIndependentRecord",
                        timeZone = "Etc/GMT+5", # use OlsonNames()
                        #stationCol = "Camera_folder", # name of the station in output file
                        video = list(file_formats = c("jpg", "mov", "avi", "mp4"),
                                      dateTimeTag = "FileModifyDate"), # to read files
                        writecsv = FALSE,
                        removeDuplicateRecords = TRUE) # removes records where there were multiple images in the same second; will be important later for subsetting images by 15 min or 60 sec or whatever

###issue with videos###

#there is stuff from all years in here...
#.AVI metadata is 13 hours earlier than timestamp on video (video correct)
#.MP4 metadata looks correct but timestamp on video is 13 hours off (metadata correct)
#.JPG metadata looks correct and matches timestamp
#exifTagNames(fileName = "")
```

```{r}
# export raw record table, to have for later
write.csv(record_table, "data/Data-21-22_Record_Table.csv", row.names = FALSE)

#Once the record table has been exported, avoid opening and editing the file in Excel!! 
# It will change the formatting of the date and time column, and R will no longer read it as a date and time (but as a string). You can correct this with as.POSIXct() if need be, but better to just not have to deal with it.
```

# Examine record table

```{r}
#which species are most common?
record_table %>% 
  group_by(Species) %>% 
  summarise(n_det = n()) %>% 
  mutate(sum(n_det)) %>% 
  arrange(desc(n_det))

#How many species per station? How long were cameras operating?
record_table %>% 
  group_by(Station) %>% 
  summarise(n_spp = n_distinct(Species), 
            n_detections = n(), 
            min_date = min(Date), 
            max_date = max(Date), 
            n_days = n_distinct(Date)) %>% 
  arrange(desc(n_detections))

#what proportion of cameras are species on?
record_table %>% 
  group_by(Station, Species) %>% 
  count() %>% 
  ungroup() %>% 
  count(Species) %>% 
  arrange(desc(n))
```

# Activity: Kernel Density Estimation

```{r}
activityDensity(recordTable = record_table,
                species     = "Snow Leopard")
activityDensity(recordTable = record_table,
                species     = "Fox")
activityDensity(recordTable = record_table,
                species     = "Markhor")
activityDensity(recordTable = record_table,
                species     = "Livestock")
```

