---
title: "CalculateCovariates"
author: "Amy Van Scoyoc"
date: "9/1/2022"
output: github_document
---

# Covariate Calculations

The camera site locations
```{r}
sitelocs <- read.csv("Site_Locs.csv")
st_as_sf(sitelocs, coords = c("Longitude", "Latitude"), crs = 4326) %>% 
st_transform(26910) -> sites_sf #it will probably need to be in the same coords as the other layers
```

Cannabis
```{r}
cannabis_2016 <- st_read("../UsefulSpatialLayers/Cannabis_2016/Cannabis_2016_C1_all.shp")

#Need to make sure that the grows from the study itself are also included...
grows <- read.csv("Grow_Locs.csv")

grows %>% 
  rename(ID = Grows) -> grows
st_as_sf(grows, coords = c("Lon", "Lat"), crs = 4326) %>% 
st_transform(26910) -> grows_sf

#have to be the same type to bind together
cannabis_2016 %>% 
  st_centroid() %>% 
  select(ID) %>% 
  rbind(grows_sf) -> all_cannabis
```

Land cover
```{r}
NLCD_2016 <- raster::raster("../UsefulSpatialLayers/Land_Cover/NLCD_JOCO/NLCD_2016_Land_Cover_L48_20190424_hJhopbp8dVByP4bBdB4q.tiff")

NLCD_key <- read_csv("../UsefulSpatialLayers/Land_Cover/NLCD2016_key.csv")
```

Rivers/Streams
```{r}
NHD <- st_read("../Ch2/Layers/JOCO_NHDplus_Flowline/JOCO_NHDplus_Flowline.shp")
NHD %>% st_zm() -> NHD
```

Elevation
```{r}
DEM_10m <- raster::raster("../Ch2/Layers/JOCO_DEM10m/JOCO_DEM10m_proj.tif")
```

Canopy cover
```{r}
cancov <- raster::raster("../UsefulSpatialLayers/GNN_cancov/rasters/cancov_2017.tif")
```

Roads
```{r}
highways <- read_sf("../UsefulSpatialLayers/Hwys_extract/Hwys_JoCo_clip.shp")
highways %>% 
  select(HWYNAME, ST_HWY_IDX) %>% 
  st_transform(26910) -> highways
```

Clearcut
```{r}
clearcuts <- read_sf("../UsefulSpatialLayers/Wilderville_Clearcuts/Wilderville_Clearcuts.kml")

clearcuts %>% 
  select(Name) %>% 
  st_zm() %>% 
  st_transform(26910) -> clearcuts
```


## Calculate

Custom function for calculating near distances
```{r}
Calculate_Near <- function(input_feature, near_feature) {
  Near_index <- st_nearest_feature(input_feature, near_feature)
  sliced <- near_feature %>% slice(Near_index)
  near_distance <- st_distance(input_feature, sliced, by_element = TRUE)
  return(near_distance)
}
```

Polygon calculations
```{r}
sites_sf %>% 
  mutate(dist_cannabis = Calculate_Near(sites_sf, all_cannabis),
         dist_NHD = Calculate_Near(sites_sf, NHD),
         dist_clearcut = Calculate_Near(sites_sf, clearcuts),
         dist_hwys = Calculate_Near(sites_sf, highways)) -> CamLocs_dists
```

Raster calculations
```{r}
# CamLocs_dists %>% 
#   mutate(elev = raster::extract(DEM_10m, CamLocs_dists),
#          NLCD = raster::extract(NLCD_2016, CamLocs_dists)) -> CamLocs_covs_sf

CamLocs_dists %>% 
  mutate(elev = raster::extract(DEM_10m, CamLocs_dists)) -> CamLocs_dists_elev
```

Creating 50m buffers around cameras
```{r}
sites_sf %>% 
  st_buffer(dist = 50) -> buffers50
```

Now, we want the proportion of forest within the buffer, as well as percent canopy cover
```{r}
buffers50 %>%
  mutate(
    cancov_avg = exactextractr::exact_extract(cancov, buffers50, 'mean'),
    #can just use the built in function for mean canopy cover
    forest_prop = exactextractr::exact_extract(NLCD_2016, buffers50,
                                               function(value, fraction) { #have to use a custom function now to get the proportion covered by any forest type
                                                 sum(fraction[value == 41 | value == 42 | value == 43], na.rm = TRUE) / sum(fraction, na.rm = TRUE)
                                               })
  ) -> buffers50_extract

```


Clean up for land cover (no longer needed)
```{r}
# CamLocs_covs_sf %>% 
#   st_drop_geometry() %>% 
#   rename(Value = NLCD) %>% 
#   left_join(NLCD_key) %>% 
#   select(-Description) %>% 
#   rename(NLCD_code = Value, NLCD_Class = Class, NLCD_Classification = Classification) %>% 
#   mutate(is_forest = if_else(NLCD_Class == "Forest", 1, 0)) -> CamLocs_covs

#write.csv(CamLocs_covs, "CamLocs_covs.csv")
```

Join and clean up
```{r}
buffers50_cleaned <- buffers50_extract %>% 
  st_drop_geometry() %>% 
  mutate(cancov_avg = cancov_avg/100) #using the scalar from the GNN readme

CamLocs_dists_elev %>% 
  st_drop_geometry() %>% 
  left_join(buffers50_cleaned) -> CamLocs_covs

#write.csv(CamLocs_covs, "CamLocs_covs.csv")
```

